---
title: "Survey1"
author: "Sayar Banerjee"
date: "1/9/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require("knitr")
opts_knit$set(root.dir = "/Users/Banner/Documents/Avanti")
```

## Removing environment variables

```{r}
rm(list=ls(all=TRUE))
```

## Load Libraries

```{r}

library(ggplot2)
library(plyr)
library(tm)
library(SnowballC)
library(wordcloud)
library(RColorBrewer)

```

## Loading in the Survey data 

```{r}
#A50 needs to be changed

Survey1<-read.csv('Avanti survey data - Data.csv', header = T,na.strings = c('-','--'))

```

## Summary of the dataset

```{r label options}

summary(Survey1)

```

## Removing redundant variables

```{r}

Survey1$X<-NULL
Survey1$ID<-NULL

```

## Changing variables into appropriate types

```{r}

Survey1$NAME<-as.character(Survey1$NAME)

Survey1$X.<-as.character(Survey1$X.)


```

## Missing values

```{r}

sort(colSums(is.na(Survey1)), decreasing = T)

```

## Renaming factors in R

### Demographic/Std. of living

```{r}

Survey1$SEX<-revalue(Survey1$SEX, replace = c("A" = "Male", "B" = "Female"))

Survey1$STATUS<-revalue(Survey1$STATUS, replace = c("A" = "Single", "B" = "Married","C" = "Widow/Widower", "D" = "Divorced/Separated"))

Survey1$R.HLD<-revalue(Survey1$R.HLD, replace = c("A" = "Head", "B" = "Wife", "C" = "Son/Daughter", "D" = "Other"))

Survey1$FINDEC<-revalue(Survey1$FINDEC, replace = c("A" = "Yes", "B" = "No"))

Survey1$AGE<-revalue(Survey1$AGE, replace = c("A" = "18-25", "B" = "25-44", "C" = "45-64", "D" = "64-80"))

Survey1$SCHL<-revalue(Survey1$SCHL, replace = c("A" = "< 5th Grade", "B" = " 5th Grade", "C" = "5th-12th Grade", "D" = "12th Grade", "E" = "Attended College/Uni", "F" = "Comp. College/Uni", "G" = "Other"))

Survey1$LIT<-revalue(Survey1$LIT, replace = c("A" = "Yes", "B" = "No"))
levels(Survey1$LOANIMP)

```

### Access to credit

```{r}

Survey1$BANK<-revalue(Survey1$BANK, replace = c("A" = "Yes", "B" = "No"))

```

## Data Vizualization

### Analysis of demographic related data

```{r}

# Plotting the distribution of the data w.r.t SEX

ggplot(data = Survey1) +
  geom_bar(mapping = aes(x = SEX, fill = SEX))

# Plotting SCHL wit SEX (Education with Sex)

ggplot(data = Survey1) +
  geom_bar(mapping = aes(x = SCHL, fill = SEX))

# Plotting LIT (literatcy)

ggplot(data = Survey1) +
  geom_bar(mapping = aes(x = LIT))

```

### Analysis of credit related data

```{r}

# Plotting STATUS with EXP (Marital Status with Expenditure)

ggplot(data = Survey1) +
  geom_boxplot(mapping = aes(x = STATUS, y = EXP))

# Plotting LOANAMT with BANK (Loan Amount with Bank)

ggplot(data = Survey1) +
  geom_boxplot(mapping = aes(x = BANK, y = LOANAMT))

# Plotting X.LOAN.1 (Source of Loans)

ggplot(data = Survey1) +
  geom_bar(mapping = aes(x = X.LOAN.1))

# Plotting %INTRST with DEBTNOW (Interest rate of loan with Debt now)

ggplot(data = Survey1) +
  geom_count(mapping = aes(x = X.INTRST, y = DEBTNOW))

# Plotting DEBTNOW with X.LOANACTV (Debt with number of active loans)

ggplot(data = Survey1) +
  geom_count(mapping = aes(x = DEBTNOW, y = X.LOANACTV))

# Plotting HYPFACT (Important factors for borrowing from a bank)

ggplot(data = Survey1) + 
  geom_bar(mapping = aes(x = HYPFACT))

```

### Analysis of Microfinance related data

```{r}

# Plotting MFI? (Asking whether individual has an idea about MFI)

ggplot(data = Survey1) +
  geom_bar(mapping = aes(x = MFI.))

# Plotting MFITIME (Duration spent with an MFI)

ggplot(data = Survey1) +
  geom_bar(mapping = aes(x = MFITIME))

# Plotting MFITRST (Trust towards MFI)

ggplot(data = Survey1) +
  geom_bar(mapping = aes(x = MFITRST))

# Plotting MFIAGAIN (Would you borrow again from an MFI?)

ggplot(data = Survey1) +
  geom_bar(mapping = aes(x = MFIAGAIN))

```

### Analysis of Avanti/Tech related data

```{r}
# Plot PHONE with PHONEWHO (Availability of smartphones vs who holds it)

ggplot(data = Survey1) +
  geom_count(mapping = aes(x = PHONE, y = PHONEWHO))

# Plot INTERNET (Access to Internet)

ggplot(data = Survey1) +
  geom_bar(mapping = aes(x = INTERNET))

# Plot GOOGLE (# of people with access to Google. Class by SEX)

ggplot(data = Survey1) +
  geom_bar(mapping = aes(x = GOOGLE, fill = SEX))

# Plot YOUTUBE (# of people with access to Youtube. Class by SEX)

ggplot(data = Survey1) +
  geom_bar(mapping = aes(x = YOUTUBE, fill = SEX))

# Plot of AVANTIFEAT (Important features about loan)

ggplot(data = Survey1) +
  geom_bar(mapping = aes(x = AVANTIFEAT))

# Plot of PHILANTHROPY (Behav. question about Avanti's motives)

ggplot(data = Survey1) +
  geom_bar(mapping = aes(x = PHILANTHROPY))

```


### STATUS VS X.HLD

```{r}
ggplot(data = Survey1) +
  geom_count(mapping  = aes(x = STATUS, y = X.HLD))

```

### INC VS EXP

```{r}
ggplot(data = Survey1) +
  geom_point(mapping = aes(x = INC, y = EXP)) +
  geom_abline()
```

### X.INTRST VS X.LOAN.1

```{r}

ggplot(data = Survey1) +
  geom_count(mapping = aes(x = X.INTRST, y = X.LOAN.1))
table(Survey1$X.LOAN.1)

```

### PHONE

```{r}

ggplot(data = Survey1) +
  geom_bar(mapping = aes(x = PHONE))

```

### combining b & c in AVANTIFEAT

### Loan Imp
```{r}
loanimp<-read.csv('LoanImp.csv', header = T)
loanimp<-as.factor(unlist(loanimp))

loanimp<-revalue(x = loanimp, replace = c("A" = "Low Interest Rates", "B" = "Friendly loan dispenser", "C" = "Known loan dispenser", "D" = "Flexible loan plan", "F" = "Reliability of loan dispenser", "E" = "Speed of loan disbursement"))

tb<-table(loanimp)
tb
loanimpdf<-as.data.frame(loanimp)

ggplot(data = loanimpdf) +
  geom_bar(mapping = aes(x = loanimp)) + 
  coord_flip()

wordcloud(words = names(tb), freq = as.numeric(tb), min.freq = 1,
          max.words=200, random.order=FALSE, scale=c(2,.3),rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
```

### hypefact

```{r}
hypefact<-read.csv('hypefact.csv',header = T)

hypefact<-as.factor(unlist(hypefact))
table(hypefact)

hypefact<-revalue(x = hypefact, replace = c("A" = "Low Interest Rates", "B" = "Friendly loan dispenser", "C" = "Known loan dispenser", "D" = "Flexible loan plan", "E" = "Distance to get loan", "F" = "Speed of loan disbursement"))

tb<-table(hypefact)
tb
hypefactdf<-as.data.frame(hypefact)

ggplot(data = hypefactdf) +
  geom_bar(mapping = aes(x = hypefact)) + 
  coord_flip()
```

### loanwhy

```{r}
loanwhy<-read.csv('loanwhy.csv',header = T,na.strings = c("-"))

loanwhy<-as.factor(unlist(loanwhy))
table(loanwhy)

loanwhy<-revalue(x = loanwhy, replace = c("A" = "Purchasing employment related G&S", "B" = "Real estate", "C" = "Healthcare", "D" = "Education", "E" = "Buying vehicles", "F" = "Emergencies", "G" = "Wedding", "H" = "Food", "I" = "Other"))

tb<-table(loanwhy)
tb
loanwhydf<-as.data.frame(loanwhy)

ggplot(data = loanwhydf) +
  geom_bar(mapping = aes(x = loanwhy)) + 
  coord_flip()

```